ZCB Pricing

### 2018-08-08 Draft.tex

\section{Introduction}
The pricing of securities is a critical task that many financial institutions must complete. In some instances, these securities have simple enough pricing equations with closed form solutions and so they can be solved analytically. A zero-coupon bond is an example of such an instrument. However, in many cases the closed form solution is not known and a numerical approach is necessary. Most options fall into this category. As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases. Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use. 
\label{sec: Intro}

>>>>

\section{Introduction}
The pricing of securities is a critical task that many financial institutions must complete. In some instances, these securities have simple enough pricing equations with closed form solutions and so they can be solved analytically. A zero-coupon bond is an example of such an instrument. However, in many cases the closed form solution is not known and a numerical approach is necessary. Most options fall into this category. As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases. Fortunately, we can make use of the fact that we know the analytical solution for a zero coupon bond to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.  
\label{sec: Intro}
